\chapter*{Abstract}

The analysis, counting and classification of white blood cells in automatic way is also an unresolved issue. This automation could be very helpful in medical field, to recognize the kind of pathology that affects a patient. Now the recognize method is completely handmade. In every medical center there is an expert that works hardly to analyse, count and classify the white blood cells in the peripheral blood.

\bigskip

His work is divide in three steps and everyone of these steps is very long. In particular we focused on a particular issue that could affect the optimal result of the work. The analyser after many hours of work due to the fatigue of sight may not sees it as well as before and maybe not see certain particulars that affect cells that could completely change the patient's diagnosis.

\bigskip

Our propose is to create a system that in automatic way is able to do every single step of the blood expert work. We want to do this in order to decrease the time and increase the efficiency of the process.

\bigskip

Our solution use a vector field VFC to describe cells edges, without using the active contour model. We choose this approach because we concentrate our work on the segmentation of the white blood cell in overlap position.

\bigskip

At the end we defined a system that is able to recognise the leukocytes by the other cells of the peripheral blood and divide the leukocytes in overlap with another one. Then in conclusion we trying to construct a method able to separate the overlapped cells, that there is the main unresolved issue of the leukocytes segmentation.


